### 2022-12-02 definitions.tex
details

@@

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility ?
\end{proposition}

>>>>

\begin{theorem}(ref)
{\sc bounded resilience} is decidable for WSTS with strong upward compatibility and effective basis of $post^*$.
\end{theorem}

We may generalyse thier result:

@@

remarque si on enlève la strong monotony:

\begin{theorem}(ref)
{\sc resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc bounded resilience} and {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility ?
\end{proposition}
